---
title: "Can you afford your dream car?"
author: "Aum Brahmbhatt"
date: "5/10/2021"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Explanation
- This app predicts if you can afford you dream car or not. 
- The prediction cannot be made without knowing your salary, MSRP of your dream car, and your debt to income ration. 
- The prediction also tell you whats the most expensive car you can buy. 

## Documentation
- Please replace the default numbers with the numbers that suits you. 
- PLEASE ONLY ENTER NUMERIC VALUES. 
- I define debt to income ratio as: Ration between all the expenses(including food, rent/house mortgage, etc) and the net income after the tax. 
- I assume that car mortgage would be 2% of the car MSRP, plus the mortgage would last for 60 months. 
- Lastly, I am aslo assuming that you are willing to spend all the income after expenses on the car mortgage for next 60 months!

## Magic Code
- This is the code that does all the magic!
- This code shows the calculation based on which it predicts if you can afford your car or not!
```{r comment="", echo = TRUE, eval = TRUE}
income <- 2500
ratio <- 25
price <- 93749
income <- income * (1-(ratio/100))
mortgage <- (price * 0.02)
price <- income/0.02
if(income > mortgage){
    outputText <- paste("CONGRATULATIONS! YOU CAN AFFORD YOUR DREAM CAR. You can buy car as expensive as", price)
}else{
    outputText<- paste("SORRY! UNFORTUNATELY YOU CAN AFFORD A CAR WITH MSRP ", price)
}
outputText
```

## Conclusion
- Hope you liked my simple app. 
- Thank for you reading along!
- I hope you can afford your dream car!
